### 2013-05-29 inst/examples/BUGS/process-noise-only.Rmd
trouble with MCMC convergence for process-noise-only
Now with longer runs and better posterior estimator. Set for run on zero.

```{r}
posterior.mode <- function(x) {
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}

@@

#Run again iteratively if we haven't met the Gelman-Rubin convergence criterion
recompile(allen_jags) # required for parallel
allen_jags <- do.call(autojags, list(object=allen_jags, n.update=10, 
                                     n.iter=n.iter, n.thin = n.thin))
```

@@

```{r allen-output, dependson="allen-traces"}
# A <- allen_posteriors
# A$index <- A$index + A$chain * max(A$index) # Combine samples across chains by renumbering index 
# pardist <- acast(A[-4], index ~ variable, subset=.(variable != "deviance") )
pardist <- acast(allen_posteriors[2:3], 1:table(allen_posteriors$variable) ~ variable, subset=.(variable!="deviance")) 
pardist[,2] = exp(pardist[,2]) # transform model parameters back first
pardist[,3] = exp(pardist[,3])
bayes_coef <- apply(pardist,2, posterior.mode) 
bayes_pars <- unname(c(bayes_coef[2], bayes_coef[1], bayes_coef[3])) # parameters formatted for f
allen_means <- sapply(x_grid, f, 0, bayes_pars)
```

>>>>

```{r}
require(modeest)
posterior.mode <- function(x) {
 # ux <- unique(x)
 #  ux[which.max(tabulate(match(x, ux)))]
 mlv(x, method="shorth")$M
}

@@

# Run again iteratively if we haven't met the Gelman-Rubin convergence criterion
recompile(allen_jags) # required for parallel
allen_jags <- do.call(autojags, list(object=allen_jags, n.update=10, 
                                     n.iter=n.iter, n.thin = n.thin))
```

@@

```{r allen-output, dependson="allen-traces"}
# A <- allen_posteriors
# A$index <- A$index + A$chain * max(A$index) # Combine samples across chains by renumbering index 
# pardist <- acast(A[-4], index ~ variable, subset=.(variable != "deviance") )
pardist <- acast(allen_posteriors[2:3], 1:table(allen_posteriors$variable)[1] ~ variable) 
pardist[,"logr0"] = exp(pardist[,"logr0"]) # transform model parameters back first
pardist[,"logtheta"] = exp(pardist[,"logtheta"])

colnames(pardist)[colnames(pardist)=="logtheta"] = "theta"
colnames(pardist)[colnames(pardist)=="logr0"] = "r0"

bayes_coef <- apply(pardist,2, posterior.mode) 
bayes_pars <- unname(c(bayes_coef["r0"], bayes_coef["K"], bayes_coef["theta"])) # parameters formatted for f
allen_means <- sapply(x_grid, f, 0, bayes_pars)
```
